Carbonate chemistry at Ny-Ålesund

### 2021-11-22 awipev-CO2.Rmd
minor changes

Depth and month of the year have a statistically significant effet on pH. The interaxction is also significant, indicating that the effect of depth differs depending on the month.

@@

### **seaFET / durafet pHs**

>>>>

Depth and month of the year have a statistically significant effect on pH. The interaction is also significant, indicating that the effect of depth differs depending on the month.

@@

### **seaFET / durafet pHs (all at 9 m)**
